---
title: "Duke Sports Analtyics: Volleyball Project (Fall 2021)"
description: |
  Exploring Duke Women's Volleyball statistics
author: Hillary Lee, Angel Chaudhary, Aditya Sardesai, Ethan Ouellette, Ashrit Verma
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = NA, tidy = "styler",
                      fig.width = 8, fig.height = 5)
```

# Introduction

Volleyball is heavily underdeveloped in terms of sports-statistics, which has
prompted us to start this project that aims to develop a WAR-like metric for
volleyball based on statistics from Duke Women's Volleyball for seasons
2018~2021. It will provide a comprehensive and hollistic approach in evaluating
players' strength and performance.

# Scraping Data

```{r packages, message = FALSE}
library(tidyverse)
```

The data is scraped from Duke Sport's website: https://goduke.com/sports/vb/stats/2021?path=vb.

```{r read-data}
url <- "https://goduke.com/sports/vb/stats/2021?path=vb"

Team_data <- xml2::read_html(url) %>% 
  rvest::html_table(fill = T) %>% 
  purrr::pluck(1) %>% 
  janitor::clean_names() %>% 
  dplyr::as_tibble()

Team_data
```

This is an explanation of the data provided on the Duke website based on the
FIVB VIS (Volleyball Information System):

| Statistic        | Description (FIVB VIS)                                                 |
|------------------|------------------------------------------------------------------------|
| Kills or Spikes  | Number of scoring attacks.                                             |
| Errors or Faults | Number of attacking errors. The opponent scores directly.              |
| Attempts         | The total number of attacks.                                           |
| Percent          | Percentage of kills out of attempts. Kills / Attempts                  |
| Kills Per Set    | Average number of scoring attacks for each set. Kills / Number of Sets |

# Analysis

# Data Visualization

# Summary
