---
title: "Duke Sports Analtyics: Volleyball Project (Fall 2021)"
description: |
  Exploring Duke Women's Volleyball statistics
author: Hillary Lee, Angel Chaudhary, Aditya Sardesai, Ethan Ouellette, Ashrit Verma
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = NA)
```

# Scraping Data

Volleyball is heavily underdeveloped in terms of sports-statistics, which has
prompted us to start this project that aims to develop a WAR-like metric for
volleyball based on statistics from Duke Women's Volleyball for seasons
2018~2021. It will provide a comprehensive and hollistic approach in evaluating
players' strength and performance.

```{r packages}
library(tidyverse)
```

The data is scraped from Duke Sport's website: https://goduke.com/sports/vb/stats/2021?path=vb.

```{r read-data}
ex_data <- read_html("https://goduke.com/sports/vb/stats/2021?path=vb")
player <- ex_data %>%
  html_nodes(".hide-on-medium-down") %>% 
  html_text()

stat <- ex_data %>%
  html_nodes(".text-center") %>%
  html_text()
```

# Analysis

# Data Visualization

# Summary
